Project Notes

### 2020-04-09 notes/notes.tex
Notes: update 07/04/2020
Notes: update 09/04/2020

@@

>>>>

\paragraph{07/04/2020}
\begin{itemize}
\item
Address ``technical debt'' in EFSM API -- it has
been inconsistent through being adapted alongside
the Node/React codegen template generation. 
Make use of dunder methods and properties
throughout to remove some of the internal logic
required in the templates.

\end{itemize}

\paragraph{08/04/2020}
\begin{itemize}
\item
Different MPST TypeSrcript encoding for Node targets --
we consider the previous encodings (labelled callbacks for
receive states, union types for send states) as ``handlers'',
and the developer needs to wrap them in an ``implementation''
class instance.

\item
The aim is for the runtime to be as lightweight as possible
-- it only needs to concern with whether the new state
is sending, receiving or terminal; and the state implementation
deals with performing the corresponding channel action
based on the particular label/payload types of that state.

\item
The class-based implementation/handler distinction allows
the runtime to use \texttt{instanceof} to safely narrow the
type of implementation. Each type of state essentially acts as
an interface (but we use classes in TypeScript to take advantage
of the \texttt{instanceof} function -- the equivalent notion
of a Java interface can be expressed as a TypeScript abstract
class with abstract methods and no properties defined). Because
all receive states will expose the same method signature,
everything type-checks.

\end{itemize}

\paragraph{09/04/2020}
\begin{itemize}
\item
Fix label regex problem in EFSM parsing -- currently just
allow alphabets, should allow more (i.e. alphanumeric
+ ``typical symbols'' like underscores and dashes).

\item
Could also look up source code of Scribble-Java to see what they use.
\end{itemize}

@@

\begin{itemize}
\item EFSM parsing -- regexes, \dots
\item EFSM API
\end{itemize}
